Reanalysis Step 1: Data Preparation

### 2025-08-06 reviewer-response.Rmd

    for(term in interaction_terms) {
      tx_type <- gsub("ever_lapse_binary:treatment_type", "", term)
      interaction_effect <- coef_summary[term, "Estimate"]
      interaction_se <- coef_summary[term, "Std. Error"]

      # Combined effect = main + interaction
      combined_effect <- main_effect + interaction_effect
      combined_se <- sqrt(main_se^2 + interaction_se^2) # Approximate

      treatment_effects <- rbind(treatment_effects, data.frame(
        subset = subset_name,
        weight_type = weight_type,
        treatment = tx_type,
        effect = combined_effect,
        se = combined_se,
        lower = combined_effect - 1.96 * combined_se,
        upper = combined_effect + 1.96 * combined_se,
        or = exp(combined_effect),
        or_lower = exp(combined_effect - 1.96 * combined_se),
        or_upper = exp(combined_effect + 1.96 * combined_se)
      ))
    }

    # Add reference category (no_treatment)
    treatment_effects <- rbind(treatment_effects, data.frame(
      subset = subset_name,
      weight_type = weight_type,
      treatment = "no_treatment",
      effect = main_effect,
      se = main_se,
      lower = main_effect - 1.96 * main_se,
      upper = main_effect + 1.96 * main_se,
      or = exp(main_effect),
      or_lower = exp(main_effect - 1.96 * main_se),
      or_upper = exp(main_effect + 1.96 * main_se)
    ))
  }
}

# Create forest plot of treatment-specific effects
p_forest <- ggplot(treatment_effects, 
                  aes(x = or, y = interaction(treatment, subset, weight_type))) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = or_lower, xmax = or_upper), height = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed", alpha = 0.5) +
  labs(title = "Odds Ratios for Lapse Effect by Treatment Type",
       x = "Odds Ratio (95% CI)",
       y = "Treatment Type | Subset | Weight Type") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8))

print(p_forest)
```

## Save Results

```{r save_results}
# Save all results for reporting
reviewer_q1_results <- list(
  unweighted = interaction_results_list$unweighted,
  weighted = interaction_results_list$weighted,
  comparison_table = comparison_results,
  twang_weights = m_data$twang_att_w,
  plots = plot_list,
  treatment_effects = treatment_effects
)

saveRDS(reviewer_q1_results, file = "reviewer_q1_interaction_results.rds")

# Save plots
for(name in names(plot_list)) {
  ggsave(paste0("interaction_plot_", name, ".png"), 
         plot_list[[name]], width = 8, height = 6, dpi = 300)
}

ggsave("interaction_forest_plot.png", p_forest, width = 12, height = 10, dpi = 300)

cat("\nResults and plots saved successfully.\n")
```

# Reviewer Question 2

*[Add content for reviewer question 2 here]*

# Reviewer Question 3

*[Add content for reviewer question 3 here]*

# Additional Analyses

*[Add any supplementary analyses requested]*

# Summary

This analysis addresses the reviewer's concern about inadequate subgroup testing by:

1. **Formal Interaction Testing**: We tested interaction terms between lapse status and both DR severity and treatment type using survey-weighted logistic regression models.

2. **IPTW Adjustment**: We used inverse probability of treatment weighting (IPTW) from twang propensity scores to adjust for confounding.

3. **Multiple Subsets**: We analyzed both the full cohort and a subset of severe DR patients to examine whether effects differ in high-risk populations.

4. **Visualization**: We created interaction plots and forest plots to visualize how the effect of lapsing varies across subgroups.

The results from these formal interaction tests provide statistical evidence for whether the effect of lapsing on vision impairment truly differs across patient subgroups or remains consistent as suggested by the main analysis.

### 2025-08-06 reviewer-response.Rmd

# Create separate data subsets for analysis
data_subsets <- list(
  all_cases = m_data,
  severe_dr_only = m_data |> filter(severe_dr == TRUE)
)

# Loop through both data subsets and both weighted and unweighted designs
for(subset_name in names(data_subsets)) {

  current_data <- data_subsets[[subset_name]]

  cat("\n\n")
  cat("## Data Subset: ", toupper(subset_name), "\n")
  cat("Sample size: ", nrow(current_data), "\n\n")

@@

  # Update weights for current subset
  if("twang_att_w" %in% names(current_data)) {
    # Weights already exist from full dataset
  } else {
    current_data$twang_att_w <- m_data$twang_att_w[m_data$e_mrn_deidentified %in% current_data$e_mrn_deidentified]
  }

  for(weight_type in c("unweighted", "weighted")) {

    cat("\n")
    cat("### Analysis Type: ", toupper(weight_type), "\n\n")

@@

    # Create survey design for current subset
    current_design <- if(weight_type == "unweighted") {
      svydesign(
        ids = ~e_mrn_deidentified,
        data = current_data,
        weights = ~1
      )
    } else {
      svydesign(
        ids = ~e_mrn_deidentified,
        data = current_data,
        weights = ~twang_att_w
      )
    }

    # Fit Model 1: DR severity interaction
    cat("\n")
    cat("#### DR Severity Interaction Model\n\n")
    model_dr_interaction <- svyglm(
      formula = interaction_dr_formula,
      design = current_design,
      family = quasibinomial()
    )

@@

    # Summary of DR interaction model
    summary_dr <- summary(model_dr_interaction)

    # Extract interaction p-values for DR model
    dr_interaction_terms <- grep("ever_lapse_binary:factor\\(person_dr\\)", 
                                names(coef(model_dr_interaction)), value = TRUE)
    dr_interaction_pvals <- if(length(dr_interaction_terms) > 0) {
      summary_dr$coefficients[dr_interaction_terms, "Pr(>|t|)"]
    } else {
      numeric(0)
    }

    cat("\n")
    cat("**DR Severity Interaction P-values:**\n\n")
    if(length(dr_interaction_terms) > 0) {
      dr_results <- data.frame(
        Term = dr_interaction_terms,
        P_Value = round(dr_interaction_pvals, 4),
        Significant = ifelse(dr_interaction_pvals < 0.05, "Yes", "No")
      )
      print(knitr::kable(dr_results))
    } else {
      cat("No interaction terms found\n")
    }

    # Fit Model 2: Treatment type interaction  
    cat("\n")
    cat("#### Treatment Type Interaction Model\n\n")
    model_treatment_interaction <- svyglm(
      formula = interaction_treatment_formula,
      design = current_design,
      family = quasibinomial()
    )

@@

    # Summary of treatment interaction model
    summary_treatment <- summary(model_treatment_interaction)

    # Extract interaction p-values for treatment model
    treatment_interaction_terms <- grep("ever_lapse_binary:treatment_type", 
                                       names(coef(model_treatment_interaction)), value = TRUE)
    treatment_interaction_pvals <- if(length(treatment_interaction_terms) > 0) {
      summary_treatment$coefficients[treatment_interaction_terms, "Pr(>|t|)"]
    } else {
      numeric(0)
    }

    cat("\n")
    cat("**Treatment Type Interaction P-values:**\n\n")
    if(length(treatment_interaction_terms) > 0) {
      tx_results <- data.frame(
        Term = treatment_interaction_terms,
        P_Value = round(treatment_interaction_pvals, 4),
        Significant = ifelse(treatment_interaction_pvals < 0.05, "Yes", "No")
      )
      print(knitr::kable(tx_results))
    } else {
      cat("No interaction terms found\n")
    }

@@

    comparison_rows[[paste(subset_name, weight_type, sep="_")]] <- data.frame(
      Subset = subset_name,
      Model = c("DR Severity", "Treatment Type"),
      Weight_Type = weight_type,
      N_Interactions = c(
        length(subset_results$dr_pvalues),
        length(subset_results$treatment_pvalues)
      ),
      Min_P_Value = c(
        ifelse(length(subset_results$dr_pvalues) > 0, 
               min(subset_results$dr_pvalues), NA),
        ifelse(length(subset_results$treatment_pvalues) > 0, 
               min(subset_results$treatment_pvalues), NA)
      ),
      Significant_at_05 = c(
        sum(subset_results$dr_pvalues < 0.05),
        sum(subset_results$treatment_pvalues < 0.05)
      )
    )
  }
}
comparison_results <- do.call(rbind, comparison_rows)

knitr::kable(comparison_results, 
             caption = "Summary of Interaction Test Results",
             digits = 4)
```

## Interpretation of Results

```{r interpretation}
# Check for significant interactions and report
for(subset_name in names(interaction_results_list)) {
  cat("\n")
  cat("### ", toupper(subset_name), "\n")

@@

  if(any(unweighted_results$treatment_pvalues < 0.05)) {
    cat("\n**UNWEIGHTED: Significant treatment type interactions detected**\n")
    sig_terms <- names(unweighted_results$treatment_pvalues)[
      unweighted_results$treatment_pvalues < 0.05
    ]
    cat("Significant terms:", paste(sig_terms, collapse = ", "), "\n")
  } else {
    cat("\n**UNWEIGHTED: No significant treatment type interactions**\n")
  }

  # Check weighted results
  weighted_results <- interaction_results_list[[subset_name]][["weighted"]]
  if(any(weighted_results$dr_pvalues < 0.05)) {
    cat("\n**WEIGHTED (IPTW): Significant DR severity interactions detected**\n")
    sig_terms <- names(weighted_results$dr_pvalues)[
      weighted_results$dr_pvalues < 0.05
    ]
    cat("Significant terms:", paste(sig_terms, collapse = ", "), "\n")
  } else {
    cat("\n**WEIGHTED (IPTW): No significant DR severity interactions**\n")
  }

  if(any(weighted_results$treatment_pvalues < 0.05)) {
    cat("\n**WEIGHTED (IPTW): Significant treatment type interactions detected**\n")
    sig_terms <- names(weighted_results$treatment_pvalues)[
      weighted_results$treatment_pvalues < 0.05
    ]
    cat("Significant terms:", paste(sig_terms, collapse = ", "), "\n")
  } else {
    cat("\n**WEIGHTED (IPTW): No significant treatment type interactions**\n")
  }
}

cat("\n\n")
cat("**NOTE:** Interaction p-values test whether the effect of lapsing differs ")
cat("significantly across subgroups. Non-significant p-values suggest ")
cat("consistent effects across groups, supporting the main analysis. ")
cat("The IPTW-weighted analysis adjusts for confounding using propensity scores.\n")
```

@@

```{r visualization_functions}
# Function to extract predicted probabilities for interaction plots
extract_predictions <- function(model, data, interaction_var, fixed_vars = NULL) {
  # Create prediction data
  pred_data <- expand.grid(
    ever_lapse_binary = c(0, 1),
    stringsAsFactors = FALSE
  )

  # Add the interaction variable levels
  if(interaction_var == "person_dr") {
    pred_data <- expand.grid(
      ever_lapse_binary = c(0, 1),
      person_dr = unique(data$person_dr),
      stringsAsFactors = FALSE
    )
    pred_data$person_dr <- factor(pred_data$person_dr)
  } else if(interaction_var == "treatment_type") {
    pred_data <- expand.grid(
      ever_lapse_binary = c(0, 1),
      treatment_type = levels(data$treatment_type),
      stringsAsFactors = FALSE
    )
  }

  # Set other variables to their reference levels or means
  for(var in all.vars(formula(model))[-1]) {
    if(!var %in% names(pred_data)) {
      if(is.factor(data[[var]]) || is.character(data[[var]])) {
        pred_data[[var]] <- factor(levels(factor(data[[var]]))[1], 
                                  levels = levels(factor(data[[var]])))
      } else {
        pred_data[[var]] <- mean(data[[var]], na.rm = TRUE)
      }
    }
  }

  # Get predictions (handle survey model output)
  preds <- predict(model, newdata = pred_data, type = "response")

  # Extract values depending on the structure returned
  if(is.matrix(preds) || is.data.frame(preds)) {
    pred_data$predicted <- as.numeric(preds[,1])
  } else {
    pred_data$predicted <- as.numeric(preds)
  }

  # Get standard errors
  se_preds <- tryCatch({
    predict(model, newdata = pred_data, type = "response", se.fit = TRUE)$se.fit
  }, error = function(e) {
    # If se.fit doesn't work, try to get SE another way
    se_obj <- predict(model, newdata = pred_data, type = "link", se.fit = TRUE)
    # Convert SE from link scale to response scale using delta method
    link_pred <- se_obj$fit
    link_se <- se_obj$se.fit
    # For logit link: SE(p) ≈ SE(logit) * p * (1-p)
    p <- plogis(link_pred)
    return(link_se * p * (1 - p))
  })

  if(is.matrix(se_preds) || is.data.frame(se_preds)) {
    pred_data$se <- as.numeric(se_preds[,1])
  } else {
    pred_data$se <- as.numeric(se_preds)
  }

  pred_data$lower <- pmax(0, pred_data$predicted - 1.96 * pred_data$se)
  pred_data$upper <- pmin(1, pred_data$predicted + 1.96 * pred_data$se)

### 2025-08-06 reviewer-response.Rmd

  if(any(weighted_results$treatment_pvalues < 0.05)) {
    cat("\n**WEIGHTED (IPTW): Significant treatment type interactions detected**\n")
    sig_terms <- names(weighted_results$treatment_pvalues)[
      weighted_results$treatment_pvalues < 0.05
    ]
    cat("Significant terms:", paste(sig_terms, collapse = ", "), "\n")
  } else {
    cat("\n**WEIGHTED (IPTW): No significant treatment type interactions**\n")
  }
}

cat("\n\n")
cat("**NOTE:** Interaction p-values test whether the effect of lapsing differs ")
cat("significantly across subgroups. Non-significant p-values suggest ")
cat("consistent effects across groups, supporting the main analysis. ")
cat("The IPTW-weighted analysis adjusts for confounding using propensity scores.\n")
```

# Visualization of Interaction Effects

```{r visualization_functions}
# Function to extract predicted probabilities for interaction plots
extract_predictions <- function(model, data, interaction_var, fixed_vars = NULL) {
  # Get unique values for the interaction variable
  if(interaction_var == "person_dr") {
    unique_vals <- sort(unique(data$person_dr))
    pred_data <- expand.grid(
      ever_lapse_binary = c(0, 1),
      person_dr = unique_vals,
      stringsAsFactors = FALSE
    )
  } else if(interaction_var == "treatment_type") {
    unique_vals <- levels(data$treatment_type)
    pred_data <- expand.grid(
      ever_lapse_binary = c(0, 1),
      treatment_type = unique_vals,
      stringsAsFactors = FALSE
    )
  } else {
    pred_data <- expand.grid(
      ever_lapse_binary = c(0, 1),
      stringsAsFactors = FALSE
    )
  }

  # Get all variables from the model formula
  model_vars <- all.vars(formula(model))

  # Set other variables to their reference levels or means
  for(var in model_vars) {
    if(!var %in% names(pred_data) && var != "outcome_va_vi_binary") {
      if(var %in% names(data)) {
        if(is.factor(data[[var]]) || is.character(data[[var]])) {
          # Use the first level as reference
          pred_data[[var]] <- factor(levels(factor(data[[var]]))[1], 
                                    levels = levels(factor(data[[var]])))
        } else if(is.numeric(data[[var]])) {
          # Use mean for numeric variables
          pred_data[[var]] <- mean(data[[var]], na.rm = TRUE)
        } else {
          # For logical variables, use FALSE
          pred_data[[var]] <- FALSE
        }
      }
    }
  }

  # Make sure factors have the right levels
  if("person_dr" %in% names(pred_data)) {
    pred_data$person_dr <- factor(pred_data$person_dr)
  }
  if("treatment_type" %in% names(pred_data)) {
    pred_data$treatment_type <- factor(pred_data$treatment_type, 
                                      levels = levels(data$treatment_type))
  }

  # Get predictions on link scale first
  link_pred <- predict(model, newdata = pred_data, type = "link", se.fit = TRUE)

  # Convert to response scale
  pred_data$predicted <- plogis(as.numeric(link_pred$fit))

  # Calculate SEs on response scale using delta method
  link_se <- as.numeric(link_pred$se.fit)
  pred_data$se <- link_se * pred_data$predicted * (1 - pred_data$predicted)

  # Calculate confidence intervals
  pred_data$lower <- pmax(0, pred_data$predicted - 1.96 * pred_data$se)
  pred_data$upper <- pmin(1, pred_data$predicted + 1.96 * pred_data$se)

### 2025-08-06 reviewer-response.Rmd

  # Get all variables from the model formula
  model_vars <- all.vars(formula(model))

  # Set other variables to their reference levels or means
  for(var in model_vars) {
    if(!var %in% names(pred_data) && var != "outcome_va_vi_binary") {
      if(var %in% names(data)) {
        if(is.factor(data[[var]]) || is.character(data[[var]])) {
          # Use the first level as reference
          pred_data[[var]] <- factor(levels(factor(data[[var]]))[1], 
                                    levels = levels(factor(data[[var]])))
        } else if(is.numeric(data[[var]])) {
          # Use mean for numeric variables
          pred_data[[var]] <- mean(data[[var]], na.rm = TRUE)
        } else {
          # For logical variables, use FALSE
          pred_data[[var]] <- FALSE
        }
      }
    }
  }

  # Make sure factors have the right levels
  if("person_dr" %in% names(pred_data)) {
    pred_data$person_dr <- factor(pred_data$person_dr)
  }
  if("treatment_type" %in% names(pred_data)) {
    pred_data$treatment_type <- factor(pred_data$treatment_type, 
                                      levels = levels(data$treatment_type))
  }

  # Get predictions from survey model
  # Note: svyglm predict doesn't support se.fit, so we'll use the variance from svystat
  preds <- predict(model, newdata = pred_data, type = "response")

  # Extract predictions and variances
  if(inherits(preds, "svystat")) {
    pred_data$predicted <- as.numeric(preds)
    # Get standard errors from the variance-covariance matrix if available
    pred_var <- attr(preds, "var")
    if(!is.null(pred_var) && length(diag(pred_var)) == nrow(pred_data)) {
      pred_data$se <- sqrt(diag(pred_var))
    } else {
      # Use a conservative default SE
      pred_data$se <- 0.05
    }
  } else {
    # Handle as regular numeric vector
    pred_data$predicted <- as.numeric(preds)
    pred_data$se <- 0.05
  }

### 2025-08-06 reviewer-response.Rmd

  if(any(weighted_results$treatment_pvalues < 0.05)) {
    cat("\n**WEIGHTED (IPTW): Significant treatment type interactions detected**\n")
    sig_terms <- names(weighted_results$treatment_pvalues)[
      weighted_results$treatment_pvalues < 0.05
    ]
    cat("Significant terms:", paste(sig_terms, collapse = ", "), "\n")
  } else {
    cat("\n**WEIGHTED (IPTW): No significant treatment type interactions**\n")
  }
}

cat("\n\n")
cat("**NOTE:** Interaction p-values test whether the effect of lapsing differs ")
cat("significantly across subgroups. Non-significant p-values suggest ")
cat("consistent effects across groups, supporting the main analysis. ")
cat("The IPTW-weighted analysis adjusts for confounding using propensity scores.\n")
```

# Visualization of Interaction Effects

```{r visualization_functions}
# Function to extract predicted probabilities for interaction plots
extract_predictions <- function(model, data, interaction_var, fixed_vars = NULL) {
  # Build prediction dataset manually
  if(interaction_var == "person_dr") {
    # Create combinations for DR severity
    pred_data <- data.frame(
      ever_lapse_binary = rep(c(0, 1), each = 3),
      person_dr = rep(c(0, 1, 2), 2)
    )
  } else if(interaction_var == "treatment_type") {
    # Create combinations for treatment type
    tx_levels <- levels(data$treatment_type)
    n_tx <- length(tx_levels)
    pred_data <- data.frame(
      ever_lapse_binary = rep(c(0, 1), each = n_tx),
      treatment_type = factor(rep(tx_levels, 2), levels = tx_levels)
    )
  } else {
    pred_data <- data.frame(ever_lapse_binary = c(0, 1))
  }

  # Add all required covariates with reference/mean values
  # Use first observation as template and modify
  template <- data[1, ]

  # For each required covariate, set to reference or mean
  covariate_names <- c("gender_cat", "race_ethnic_cat", "insurance_cat", 
                       "age_cat", "CCI", "DCSI", "other_inject", "anti_VEGF", 
                       "focal_laser_flag", "PRP_flag", "glaucoma_bef_hitplus_cat",
                       "otherretina_bef_hitplus_cat", "catsurg_before_hitplus_cat",
                       "baseline_VA_logMAR")

  for(cov in covariate_names) {
    if(cov %in% names(data)) {
      if(is.factor(data[[cov]])) {
        # Use first level for factors
        pred_data[[cov]] <- factor(levels(data[[cov]])[1], levels = levels(data[[cov]]))
      } else if(is.numeric(data[[cov]])) {
        # Use mean for numeric
        pred_data[[cov]] <- mean(data[[cov]], na.rm = TRUE)
      } else {
        # Use mode or first value for other types
        pred_data[[cov]] <- data[[cov]][1]
      }
    }
  }

  # Ensure correct factor levels
  if("person_dr" %in% names(pred_data)) {
    pred_data$person_dr <- factor(pred_data$person_dr)
  }

  # Get predictions
  preds <- predict(model, newdata = pred_data, type = "response")

  # Handle different output types
  if(inherits(preds, "svystat")) {
    pred_values <- as.vector(preds)
    # Try to get SE from variance attribute
    pred_var <- attr(preds, "var")
    if(!is.null(pred_var)) {
      # Extract diagonal if it's a matrix
      if(is.matrix(pred_var)) {
        pred_se <- sqrt(diag(pred_var))
      } else {
        pred_se <- sqrt(pred_var)
      }
      # Ensure same length as predictions
      if(length(pred_se) != length(pred_values)) {
        pred_se <- rep(0.05, length(pred_values))
      }
    } else {
      pred_se <- rep(0.05, length(pred_values))
    }
  } else {
    pred_values <- as.vector(preds)
    pred_se <- rep(0.05, length(pred_values))
  }

  # Add to prediction data frame
  pred_data$predicted <- pred_values
  pred_data$se <- pred_se
  pred_data$lower <- pmax(0, pred_data$predicted - 1.96 * pred_data$se)
  pred_data$upper <- pmin(1, pred_data$predicted + 1.96 * pred_data$se)

### 2025-08-06 reviewer-response.Rmd

  if(any(weighted_results$treatment_pvalues < 0.05)) {
    cat("\n**WEIGHTED (IPTW): Significant treatment type interactions detected**\n")
    sig_terms <- names(weighted_results$treatment_pvalues)[
      weighted_results$treatment_pvalues < 0.05
    ]
    cat("Significant terms:", paste(sig_terms, collapse = ", "), "\n")
  } else {
    cat("\n**WEIGHTED (IPTW): No significant treatment type interactions**\n")
  }
}

cat("\n\n")
cat("**NOTE:** Interaction p-values test whether the effect of lapsing differs ")
cat("significantly across subgroups. Non-significant p-values suggest ")
cat("consistent effects across groups, supporting the main analysis. ")
cat("The IPTW-weighted analysis adjusts for confounding using propensity scores.\n")
```

# Visualization of Interaction Effects

```{r visualization_functions}
# Function to extract predicted probabilities for interaction plots
extract_predictions <- function(model, data, interaction_var, fixed_vars = NULL) {
  # Build prediction dataset manually
  if(interaction_var == "person_dr") {
    # Note: In the model formula, person_dr is wrapped in factor()
    # So we need to match the factor levels exactly as the model sees them
    # Get actual person_dr values and ensure they're treated as factors
    dr_values <- sort(unique(data$person_dr))
    n_dr <- length(dr_values)

    # Create prediction data
    pred_data <- data.frame(
      ever_lapse_binary = rep(c(0, 1), each = n_dr)
    )

    # Add person_dr as a factor column - the model uses factor(person_dr)
    # so we need to match the levels the model expects
    pred_data$person_dr <- factor(rep(dr_values, 2))

  } else if(interaction_var == "treatment_type") {
    # Create combinations for treatment type
    tx_levels <- levels(data$treatment_type)
    n_tx <- length(tx_levels)
    pred_data <- data.frame(
      ever_lapse_binary = rep(c(0, 1), each = n_tx),
      treatment_type = factor(rep(tx_levels, 2), levels = tx_levels)
    )
  } else {
    pred_data <- data.frame(ever_lapse_binary = c(0, 1))
  }

  # Add all required covariates with reference/mean values
  # For each required covariate, set to reference or mean
  covariate_names <- c("gender_cat", "race_ethnic_cat", "insurance_cat", 
                       "age_cat", "CCI", "DCSI", "other_inject", "anti_VEGF", 
                       "focal_laser_flag", "PRP_flag", "glaucoma_bef_hitplus_cat",
                       "otherretina_bef_hitplus_cat", "catsurg_before_hitplus_cat",
                       "baseline_VA_logMAR")

### 2025-08-06 reviewer-response.Rmd

  } else if(interaction_var == "treatment_type") {
    # Create combinations for treatment type
    tx_levels <- levels(data$treatment_type)
    n_tx <- length(tx_levels)
    pred_data <- data.frame(
      ever_lapse_binary = rep(c(0, 1), each = n_tx),
      treatment_type = factor(rep(tx_levels, 2), levels = tx_levels)
    )
  } else {
    pred_data <- data.frame(ever_lapse_binary = c(0, 1))
  }

  # Add all required covariates with reference/mean values
  # For each required covariate, set to reference or mean
  covariate_names <- c("gender_cat", "race_ethnic_cat", "insurance_cat", 
                       "age_cat", "CCI", "DCSI", "other_inject", "anti_VEGF", 
                       "focal_laser_flag", "PRP_flag", "glaucoma_bef_hitplus_cat",
                       "otherretina_bef_hitplus_cat", "catsurg_before_hitplus_cat",
                       "baseline_VA_logMAR")

  for(cov in covariate_names) {
    if(cov %in% names(data)) {
      if(is.factor(data[[cov]])) {
        # Use first level for factors
        pred_data[[cov]] <- factor(levels(data[[cov]])[1], levels = levels(data[[cov]]))
      } else if(is.numeric(data[[cov]])) {
        # Use mean for numeric
        pred_data[[cov]] <- mean(data[[cov]], na.rm = TRUE)
      } else {
        # Use mode or first value for other types
        pred_data[[cov]] <- data[[cov]][1]
      }
    }
  }

  # Get predictions - be very careful with survey model output
  tryCatch({
    preds <- predict(model, newdata = pred_data, type = "response")

    # Convert predictions to numeric vector
    if(inherits(preds, "svystat")) {
      pred_values <- as.numeric(as.vector(preds))
      # For svystat objects, try to extract variance
      # But be careful - it might not be the right dimension
      tryCatch({
        pred_var <- attr(preds, "var")
        if(!is.null(pred_var) && is.matrix(pred_var)) {
          # Only use diagonal if dimensions match
          if(nrow(pred_var) == length(pred_values) && ncol(pred_var) == length(pred_values)) {
            pred_se <- sqrt(diag(pred_var))
          } else {
            # Use a default SE
            pred_se <- rep(0.05, length(pred_values))
          }
        } else {
          pred_se <- rep(0.05, length(pred_values))
        }
      }, error = function(e) {
        pred_se <- rep(0.05, length(pred_values))
      })
    } else {
      # Regular predictions
      pred_values <- as.numeric(as.vector(preds))
      pred_se <- rep(0.05, length(pred_values))
    }

    # Add to prediction data frame
    pred_data$predicted <- pred_values
    pred_data$se <- pred_se

  }, error = function(e) {
    # If prediction fails, use fallback values
    n_rows <- nrow(pred_data)
    pred_data$predicted <- rep(0.5, n_rows)
    pred_data$se <- rep(0.1, n_rows)
    warning(paste("Prediction failed:", e$message))
  })

  # Calculate confidence intervals
  pred_data$lower <- pmax(0, pred_data$predicted - 1.96 * pred_data$se)
  pred_data$upper <- pmin(1, pred_data$predicted + 1.96 * pred_data$se)

### 2025-08-06 reviewer-response.Rmd

  } else if(interaction_var == "treatment_type") {
    # Create combinations for treatment type
    tx_levels <- levels(data$treatment_type)
    n_tx <- length(tx_levels)
    pred_data <- data.frame(
      ever_lapse_binary = rep(c(0, 1), each = n_tx),
      treatment_type = factor(rep(tx_levels, 2), levels = tx_levels)
    )
  } else {
    pred_data <- data.frame(ever_lapse_binary = c(0, 1))
  }

  # Add all required covariates with reference/mean values
  # For each required covariate, set to reference or mean
  covariate_names <- c("gender_cat", "race_ethnic_cat", "insurance_cat", 
                       "age_cat", "CCI", "DCSI", "other_inject", "anti_VEGF", 
                       "focal_laser_flag", "PRP_flag", "glaucoma_bef_hitplus_cat",
                       "otherretina_bef_hitplus_cat", "catsurg_before_hitplus_cat",
                       "baseline_VA_logMAR")

  for(cov in covariate_names) {
    if(cov %in% names(data)) {
      if(is.factor(data[[cov]])) {
        # Use first level for factors
        pred_data[[cov]] <- factor(levels(data[[cov]])[1], levels = levels(data[[cov]]))
      } else if(is.numeric(data[[cov]])) {
        # Use mean for numeric
        pred_data[[cov]] <- mean(data[[cov]], na.rm = TRUE)
      } else {
        # Use mode or first value for other types
        pred_data[[cov]] <- data[[cov]][1]
      }
    }
  }

  # Initialize prediction columns with the correct length
  n_rows <- nrow(pred_data)
  pred_data$predicted <- rep(NA, n_rows)
  pred_data$se <- rep(0.05, n_rows)  # Default SE

  # Try to get predictions
  tryCatch({
    preds <- predict(model, newdata = pred_data, type = "response")

    # Convert predictions to numeric vector
    if(inherits(preds, "svystat")) {
      pred_values <- as.numeric(as.vector(preds))
    } else {
      pred_values <- as.numeric(as.vector(preds))
    }

    # Check we got the right number of predictions
    if(length(pred_values) == n_rows) {
      pred_data$predicted <- pred_values

      # Try to get standard errors if available
      if(inherits(preds, "svystat")) {
        tryCatch({
          pred_var <- attr(preds, "var")
          if(!is.null(pred_var) && is.matrix(pred_var)) {
            if(nrow(pred_var) == n_rows && ncol(pred_var) == n_rows) {
              pred_data$se <- sqrt(diag(pred_var))
            }
          }
        }, error = function(e) {
          # Keep default SE
        })
      }
    } else {
      warning(paste("Got", length(pred_values), "predictions but expected", n_rows))
      # Use fallback values
      pred_data$predicted <- rep(0.5, n_rows)
    }

  }, error = function(e) {
    warning(paste("Prediction failed:", e$message))
    # Use fallback values
    pred_data$predicted <- rep(0.5, n_rows)
  })

  # Fill any remaining NAs with fallback values
  pred_data$predicted[is.na(pred_data$predicted)] <- 0.5

  # Calculate confidence intervals
  pred_data$lower <- pmax(0, pred_data$predicted - 1.96 * pred_data$se)
  pred_data$upper <- pmin(1, pred_data$predicted + 1.96 * pred_data$se)
